Combinatorial Identities from Lagrange's Interpolation Polynomial

### 2020-12-03 article120120.tex
120320 update on topic and intro

\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置
%\usepackage{times}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{tabularx,array}
\usepackage{pgf,tikz}
 \usepackage{blkarray} %line 80-92 Q formula matrix index
%\usepackage{colortbl}
\usepackage{enumitem}% enumerate labels   roman
\usetikzlibrary{arrows}
\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
\date{} %不要日期

@@

\begin{defn} \cite{prn_fros1}
    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
        of $C$ is defined by 
        $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
    where $|\lambda|$ is the magnitude of complex number $\lambda.$
\end{defn}

Perron–Frobenius theorem
\begin{thm} \cite{chang} \cite{prn_fros2}
    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
    eigenvalue of $C$ with a corresponding nonnogative right eigenvector and a
    corresponding nonnegative left eigenvector.
\end{thm}

@@

\begin{defn} 
    Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square 
    matrix $A = (a_{ij})$ indexed by vertices of G, and
     \[a_{ij} =\begin{cases} 
        1, \text{if $i$ is adjacent to $j$}, \\
        0, \text{otherwise.}
            \end{cases}
     \]
\end{defn}

@@

We introduce two matrices $P$ and $Q$ in the following theorem, where $P$ is a permutation
 matrix which is multiplied to the left side, and $Q$ is sum of elementary matrix and
 certain binary matrix. In which $P$ generalize row permutation on cases of $C$
 matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns
  and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C\leq C'$

The following theorem is from \cite{chang}.

@@

\begin{proof}
    Multiplying the nonnegative vector $u$ in theorem~\ref{pre_thm} assumption
    ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
    ~\ref{pre_thm_em1},    
    \begin{equation}\label{pre1}
       PCQu\leq PC'Qu=\lambda'PQu.
    \end{equation}
    Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
    left eigenvector of $C$ for $\lambda$, thus we have
    \begin{equation}\label{pre2}
        \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
    \end{equation}
        Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
        $\lambda\leq \lambda'$ and finish the proof of the first part.
        Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
        Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence,
        $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
        $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
         \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
\end{proof}

\section{Our Method}
We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$. We will apply the previous theorem \ref{pre_thm} with $P=I$ and

@@

\begin{defn}%[$k$-rooted vector]
~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}\label{lem:rt_vec}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}[label=(\roman*)]
\item \label{lem:rt_vec:en1}$v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
% \qed
\end{lem}

Below is our first result, in which the first condition implies the first n-1 columns of C major to
 the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
 suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
  but with the same meaning with theorem (\ref{pre_thm})
\begin{thm}\label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}[label=(\roman*)]
\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item \label{thm_main:condition_ii} there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item \label{thm_main:condition_iv}$v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}[label=(\alph*)]
    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} %\qed
\end{thm}
%

% {}

\begin{proof}
    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1}). 
    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this theorem. 
    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
     Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this theorem since $P = I$ and
       $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
        $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this theorem. 
\end{proof}

We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
Motivated by the condition (i) of theorem 2.3, we provide the following two definitions. 
This is the definition of (k,n)-sum.
\begin{defn}
    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
\end{defn}

Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
Below is the definition of k-rooted matrix.
\begin{defn}\label{m_rooted}
    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $k-rooted$ except the last column of $C'$.
\end{defn}

@@

The following theorem shows that a $k$-rooted matrix has a $k$-rooted eigenvector.
\begin{lem}\label{lma_m_rooted}
    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
        \begin{enumerate}[label=(\roman*)]
            \item $C'$ is a $k$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
            \item Assume that $C'$ is $k$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
                for $\rho(C')$. Then  $C'$ has a $k$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
            \item $\rho(C')$ = $\rho(Q^{-1}C'Q)$
        \end{enumerate}
\end{lem}

@@

\begin{rem}
        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
        1 &  & & &  & 0 \\
         & 1 &  &      &  &  \\
         &  & \ddots & &  & -1 \\
         &  &        & &  &  \\
          &  & & & 1 &  \\
        0 &  & & &  & 1 \\
        \end{pmatrix},$$
\end{rem}
\end{comment}   
\begin{proof}
    (i)
    and $Q^{-1}C'Q$ is
    $$\begin{pmatrix}
    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
    \vdots \\
    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    (ii)
        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $k$-rooted.  
        Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
        $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
        $C'Qu=\rho(C')Qu$.

@@

\begin{thm}
    Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
    such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
    $r'_k \geq r'_n$. Moreover choose $c'_{in}:=r'_i-c'_{ik}$. Then $\rho(C)\leq \rho(C')$, when $C'=(c'_{ij})$.
\end{thm}

\begin{proof}
    These assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
    (\ref{lma_m_rooted});\\
    calculation:  \\
       \\
    by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
     a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same
      eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
       conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
        then $\rho(C') \geq \rho(C)$  %\qed
\end{proof}

\subsection{Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$
    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of theorem~\ref{thm_main},
    Then
    $\rho(C)\leq \rho(C')$ by previous theorem.

@@

\bibitem{prn_fros1}
A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012

@@

>>>>

\usepackage{fontspec}   %加這個就可以設定字體
\usepackage{xeCJK}       %讓中英文字體分開設置
%\usepackage{times}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{ulem}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{tabularx,array}
\usepackage{pgf,tikz}
 \usepackage{blkarray} %line 80-92 Q formula matrix index
%\usepackage{colortbl}
\usepackage{enumitem}% enumerate labels   roman
\usepackage{graphicx}
\graphicspath{{images/}}
\usetikzlibrary{arrows}
\setCJKmainfont{標楷體} %設定中文為系統上的字型，而英文不去更動，使用原TeX字型
\XeTeXlinebreaklocale "zh"             %這兩行一定要加，中文才能自動換行
\XeTeXlinebreakskip = 0pt plus1pt     %這兩行一定要加，中文才能自動換行
\title{Combinatorial Identities from Lagrange's Interpolation Polynomial}
\author{Student: Yen-Jung Huang  ~~~~~~~~~~~~~~~~~~~~~~~~~~Advisor: Chih-Wen Weng}
\date{} %不要日期

@@

\begin{defn} \cite{spec_rad}
    When $C$ is an $n \times n$ real matrix, the $\textit {spectral radius} $ $\rho(C)$
        of $C$ is defined by 
        $$\rho(C):=\max\{~|\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
    where $|\lambda|$ is the magnitude of complex number $\lambda.$
\end{defn}

The next theorem is Perron–Frobenius Theorem, which provides a feature of
 nonnegative eigenvector to nonnegative matrices.
\begin{thm} \cite{chang} \cite{prn_fros2} \label{thm:Perron_Frobenius}
    If $C$ is nonnegative square matrix, then the spectral radius $\rho(C)$ is an
    eigenvalue of $C$ with a corresponding nonnegative right eigenvector and a
    corresponding nonnegative left eigenvector.
\end{thm}

@@

\begin{defn} 
    Given an directed graph G, the$\textit{ adjacency matrix}$ of G is the square 
    matrix $A = (a_{ij})$ indexed by vertices of G, and
     \[a_{ij} =\begin{cases} 
        1, \text{if $i$ is adjacent to $j$}, \\
        0, \text{otherwise.}
            \end{cases}
     \]
\end{defn}

@@

We introduce two matrices $P$ and $Q$ in the following Theorem, where $P$ is a permutation
 matrix which is multiplied to the left side, and $Q$ is sum of elementary matrix and
 certain binary matrix. In which $P$ generalize row permutation on cases of $C$
 matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns
  and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C\leq C'$

The following Theorem is from \cite{chang}.

@@

\begin{proof}
    Multiplying the nonnegative vector $u$ in Theorem~\ref{pre_thm} assumption
    ~\ref{pre_thm_em1}, where $Qu$ is eigenvector of $C'$,  to the right of both terms of
    ~\ref{pre_thm_em1},    
    \begin{equation}\label{pre1}
       PCQu\leq PC'Qu=\lambda'PQu.
    \end{equation}
    Multiplying the nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption
     ~\ref{pre_thm_em3} to the left of all terms  in (\ref{pre1}), where $v^TP$ is
    left eigenvector of $C$ for $\lambda$, thus we have
    \begin{equation}\label{pre2}
        \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
    \end{equation}
        Now delete the positive term $v^TPQu$ by assumption \ref{pre_thm_em4} to obtain
        $\lambda\leq \lambda'$ and finish the proof of the first part.
        Assume that $\lambda=\lambda'$, so the inequality in (\ref{pre2}) is an equality.
        Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i\not=0.$ Hence,
        $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$ with
        $u_j\not=0.$ Conversely, (\ref{pre0}) implies $$v^TPCQu=\sum_{i,j} v_i(PCQ)_{ij}u_j=
         \sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so $\lambda=\lambda'$ by (\ref{pre2}).
\end{proof}

\section{Our Method}
We use $[n-1]$ as notation of the set of elements from one to $n-1$, which is ${1,2,...,n}$.
Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ 
appearing in the position $k,n$ of $E_{kn}$. We will apply the previous Theorem \ref{pre_thm} with $P=I$ and

@@

\begin{defn}%[$K$-rooted vector]
~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $K$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}\label{lem:rt_vec}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}[label=(\roman*)]
\item \label{lem:rt_vec:en1}$v'$ is $K$-rooted  if and only if  $u$ is nonnegative;
\item $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
% \qed
\end{lem}

Below is our first result, in which the first condition implies the first n-1 columns of C major to
 the columns of C', and the (k,n)-sum column of C is also major to C'. The second and the third condition
 suggest that C and C' have nonnegative eigenvectors which are k-rooted. And the forth condition is simplier
  but with the same meaning with Theorem (\ref{pre_thm})
\begin{thm}\label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}[label=(\roman*)]
\item \label{thm_main:condition_i} $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item \label{thm_main:condition_ii} there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item \label{thm_main:condition_iii}there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item \label{thm_main:condition_iv}$v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}[label=(\alph*)]
    \item \label{thm_main:equ_cond_a} $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
    \item \label{thm_main:equ_cond_b} $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
    \item \label{thm_main:equ_cond_c} $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} %\qed
\end{thm}
%

\begin{proof}
    The proof is based on Theorem~\ref{pre_thm} with $P = I$ and $Q = I + E_{kn}$ in (\ref{Q_1}). 
    The assumption \ref{pre_thm_em1} $PCQ\leq PC'Q$ of Theorem~\ref{pre_thm} holds by the condition \ref{thm_main:condition_i} of this Theorem. 
    Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition \ref{thm_main:condition_ii} and
     Lemma~\ref{lem:rt_vec}\ref{lem:rt_vec:en1}. Hence the assumption \ref{pre_thm_em2} of Theorem~\ref{pre_thm} holds. The assumptions \ref{pre_thm_em3} and \ref{pre_thm_em4}
      of Theorem~\ref{pre_thm} clearly hold by conditions~\ref{thm_main:condition_iii},\ref{thm_main:condition_iv} of this Theorem since $P = I$ and
       $v'= Qu$  Hence $\lambda \leq \lambda' $ by the necessary condition of Theorem~\ref{pre_thm}. Moreover
        $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
         conditions \ref{thm_main:equ_cond_a},\ref{thm_main:equ_cond_b},\ref{thm_main:equ_cond_c} of this Theorem. 
\end{proof}

We are interested in the matrices $C'$ that have $K$-rooted eigenvectors.
Motivated by the condition (i) of Theorem 2.3, we provide the following two definitions. 
This is the definition of (k,n)-sum.
\begin{defn}
    For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-sum vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
\end{defn}

Note that the last column of $C'Q$ is the $(k, n)$-sum vector of $C'$
Below is the definition of k-rooted matrix.
\begin{defn}\label{m_rooted}
    A  matrix $C'=(c'_{ij})$ is called $k-rooted$  if its  columns and its $(k, n)$-sum vector are all $K$-rooted except the last column of $C'$.
\end{defn}

@@

The following Theorem shows that a $K$-rooted matrix has a $K$-rooted eigenvector.
\begin{lem}\label{lma_m_rooted}
    Let $C'=(c'_{ij})$ be an $n\times n$ nonnegative matrix. Then the following (i)-(iii) hold.
        \begin{enumerate}[label=(\roman*)]
            \item \label{lma_m_rooted_cond1} $C'$ is a $K$-rooted matrix, if and only if, $Q^{-1}C'Q$ is nonnegative.
            \item \label{lma_m_rooted_cond2}Assume that $C'$ is $K$-rooted and let $u$ be a nonnegative eigenvector of $Q^{-1}C'Q$
                for $\rho(C')$. Then  $C'$ has a $K$-rooted eigenvector $v'=Qu$ for $\rho(C')$. 
            \item \label{lma_m_rooted_cond3}$\rho(C')$ = $\rho(Q^{-1}C'Q)$
        \end{enumerate}
\end{lem}

@@

\begin{rem}
        (i) is immediate from Definition~\ref{m_rooted} and the observation that   
        $$Q^{-1}=I-E_{kn}=\begin{pmatrix}
        1 &  & & &  & 0 \\
         & 1 &  &      &  &  \\
         &  & \ddots & &  & -1 \\
         &  &        & &  &  \\
          &  & & & 1 &  \\
        0 &  & & &  & 1 \\
        \end{pmatrix},$$
\end{rem}
\end{comment}   
\begin{proof}
    (i)
    and $Q^{-1}C'Q$ is
    $$\begin{pmatrix}
    c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
    \vdots \\
    c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
    c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
    c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
    \vdots              & \vdots & \ddots              & \vdots & \vdots \\
    c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    (ii)
        By Lemma~\ref{lem:rt_vec} $v'=Qu$ is $K$-rooted.  
        Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
        $Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
        $C'Qu=\rho(C')Qu$.

@@

\begin{thm}\label{thm:conclusion}
    Let $C$ be an $n\times n$ nonnegative matrix. For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$
    such that $c'_{ij}\geq c_{ij}$ and $c'_{kj}\geq c'_{nj}>0$, and choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, and
    $r'_k \geq r'_n$. Moreover choose $c'_{in}:=r'_i-c'_{ik}$. Then $\rho(C)\leq \rho(C')$, when $C'=(c'_{ij})$.
\end{thm}

\begin{proof}
    These assumptions are necessary that $PCQ \leq PC'Q$ where $P = I$,$Q = I+E_{kn}$. And $C'$ is $K$-rooted,based on Lemma
     (\ref{lma_m_rooted}),\\
    $Q^{-1}C'Q$ = 
    $$\begin{pmatrix}
        c'_{11}     & c'_{12} & \cdots     & c'_{1\ n-1} & c'_{1k}+c'_{1n} \\
        \vdots \\
        c'_{k-11}     & c'_{k-1 2}           & \cdots     & c'_{k-1 n-1} & c'_{k-1k}+c'_{k-1n} \\
        c'_{k1}-c'_{n1} & c'_{k2}-c'_{n2} &\cdots      &c'_{kn-1}-c'_{nk-1}& c'_{kk}+c'_{kn}-c'_{nk}-x'_{nn}\\
        c'_{k+11}     & c'_{k+12}           & \cdots     & c'_{k+1\ n-1} & c'_{k+1k}+c'_{k+1n} \\
        \vdots              & \vdots & \ddots              & \vdots & \vdots \\
        c'_{n1}             & c'_{n2} & \cdots             & c'_{n\ n-1} & c'_{nk}+c'_{nn} \\
    \end{pmatrix}.$$
    $Q^{-1}C'Q \geq 0$ for that $c'_{kj}\geq c'_{nj}>0$ when $1\leq j\leq n-1$ , $c'_{ij}\geq c_{ij}$ where $C$ is nonnegative,
    and the last column $c'_{in}+c'_{ik}=r'_i \geq c_{in}+c_{ik}$ by assumption $r'_i\geq c_{ik}+c_{in}$\\

    For $1\leq i \leq n$ and $1\leq j\leq n-1$, choose $c'_{ij}$ such that $c'_{ij}\geq c_{ij}$, \\
    which implies $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ \\
    And under the same condition for $i$ and $j$, choose $r'_i$ such that $r'_i\geq c_{ik}+c_{in}$, \\
    which implies $c_{ik}+c_{in}\leq c'_{ik}+c'_{in} = r'_i$ ;\\
    $C'$ is $K$-rooted matrix, then by Lemma (\ref{lma_m_rooted}) Conditions \ref{lma_m_rooted_cond2} and \ref{lma_m_rooted_cond3}, there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
    such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;\\
    And since $C$ is nonnegative, by Theorem~(\ref{thm:Perron_Frobenius}), which is Perron–Frobenius theorem, we claim there exists
    $v^T = w^{T}P$, such that $v^T$ is nonnegative left eigenvector of $C$, and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ 
    is an eigenvalue of $C$ with associated left eigenvector $v^T$; \\
    Due to $v'$ and $v^T$ are nonnegative, $v^Tv'>0.$, unless they are orthogonal, i.e, $v^Tv'=0$.\\[1ex]
    Here we can summerize the facts we know so far as the following: \\
    \begin{enumerate}[label=(\roman*)]
        \item  $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
        \item  there exists a $K$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
        such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
        \item there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
        \item $v^Tv'>0.$
    \end{enumerate}
    which come from Theorem~(\ref{thm_main}).\\
    By Lemma~(\ref{l_diag}), for certain $d$, if $C'+dI$ is $K$-rooted, then it has
    a $K$-rooted eigenvector with its spectral radius $\lambda + d$. $C'$ would share the same
    eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
    conditions of Theorem~(\ref{thm_main}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
    then $\rho(C') \geq \rho(C)$  %\qed
\end{proof}

\subsection{Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    And its corresponding graph,\cite[sage]{sage}\\
    \includegraphics{graph_C.PNG} \\
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$
    also, graph,\cite[sage]{sage}\\
    \includegraphics{graph_Cprime.PNG} \\
    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ of Theorem~\ref{thm_main},
    Then
    $\rho(C)\leq \rho(C')$ by previous Theorem~\ref{thm:conclusion}.

@@

\bibitem{spec_rad}
A. E. Brouwer, W. H. Haemers, {\it Spectra of graphs}, Springer, 2012

@@

\bibitem{sage}
[Sage] SageMath, the Sage Mathematics Software System (Version 8.7),
       The Sage Developers, 2019, https://www.sagemath.org.  %sage tutorial
